### 2023-10-17 ms.qmd
pmcmc function and some exampeles

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms)
```

@@

dharma(GMM_deli2)
install.packages("lmtest")
library(lmtest)
lrtest(null, GMM_deli)
anova(GMM_deli)
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
  facet_grid(as.factor(deli_associative$group)) + labs(y = "Colour Association Task", x = "Trial")
print(plot_deli)
```

>>>>

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here)

source(here("R", "func.R"))
```

@@

pmcmc(temp23 - temp28)
dharma(GMM_deli2)
install.packages("lmtest")
library(lmtest)
lrtest(null, GMM_deli)
anova(GMM_deli)
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
  facet_grid(as.factor(deli_associative$group)) + labs(y = "Colour Association Task", x = "Trial")
print(plot_deli)
```
